### 2021-09-20 README.Rmd
update README

This research compendium has been developed using the statistical programming
language R. To work with the compendium, you will need
installed on your computer the [R software](https://cloud.r-project.org/)
itself and optionally [RStudio Desktop](https://rstudio.com/products/rstudio/download/).

>>>>

This compendium can be accessed in a web browser using binder...

This research compendium has been developed using the statistical programming
language R. To work with the compendium locally, you will need
installed on your computer the [R software](https://cloud.r-project.org/)
itself and optionally [RStudio Desktop](https://rstudio.com/products/rstudio/download/).
